Performance Comparison of Common Face Detection APIs using Video Stills from Professional Tennis Matches

### 2018-02-16 paper/paper.Rmd
Sample and software section edits

##Sample and sampling approach

Images from the Australian Open 2016 were provided by Tennis Australia, with the following specs: 6406 images, 800 $\times$ 450px

Images were derived from, 5 minute segments taken from 105 video files, with a still shot stored every three seconds. The video files used were the broadcasts of the tennis matches shown on the Seven Network during the Australian Open 2016. The sample included an equal amount of females and males singles tennis matches.
Images contained the faces of many people, such as players, staff on the court and fans in the crowd. The sample was not filtered at this initial stage.
Matches played during the Australian Open are played on a range of courts available at Melbourne Olympic Park. The sample was selected to be representative of the seven courts that have the Hawk Eye technology enabled.

##Software selection

@@

##Software usage

The face recognition software APIs were accessed via a R [@R] script, calling the APIs relied on the httr [@httr] package. The scripts looped through the images, individually posting a request to retrieve information provided and convert it into an appropriate format for analysis. Special handling was required due to the limits on requests per minute of Skybiometry and Microsoft, time-controlling and error management of the requests was incorporated for these APIs.

Figure \ref{fig:timeFigure} shows the distribution of processing time required by the APIs for each image. The violin plot display created by @Violin 'combines the box plot and the density'. A categorical variable splits the data along the x axis, as would be seen in a box plot display. A density plot is then incorporated on the y axis. This is produced by manipulating a density display; switching the axes allows the continuous variable to increase along on the y axis, then the violin shape is created by mirroring the density. The width of the violin will now be twice the length that would be have been measured vertically in a density plot.

As seen in the facets of Figure \ref{fig:timeFigure}, both Microsoft and Google had few images which took a significant amount of time to complete, and these were removed from this plot due to concerns regarding the network. The times taken to search are quite variable between APIs, with Skybiometry consistently spending less time than other APIs. Microsoft and Google's times vary regardless of the number of faces found. The lines overlaid in each plot represent the smoothed linear model of the amount of faces, it can be seen that all APIs take longer to complete detection of faces in an image when there are more faces. As all APIs had more images where only one or two faces were found it resulted in more variability in the amount of time taken.

>>>>

## Sample and sampling approach

Images from the Australian Open 2016 were provided by Tennis Australia. There were 6406 images, 800 $\times$ 450px.
The images were derived from 5 minute segments taken from 105 video files, with a still shot stored every three seconds. The video files used were the broadcasts of the tennis matches shown on the Seven Network during the Australian Open 2016. The sample included an equal amount of females and males singles tennis matches.
Images contained the faces of many people, such as players, staff on the court and fans in the crowd.

## Software selection

@@

##Software Processing Time

The face recognition software APIs were accessed via a R [@R] script, calling the APIs relied on the httr [@httr] package. Special handling was required due to the limits on requests per minute of Skybiometry and Microsoft, time-controlling and error management of the requests was incorporated for these APIs.

Figure \ref{fig:timeFigure} shows the distribution of processing time required by the APIs for each image. The violin plot display created by @Violin 'combines the box plot and the density'. A categorical variable splits the data along the x axis, as would be seen in a box plot display. A density plot is then incorporated on the y axis. This is produced by manipulating a density display; switching the axes allows the continuous variable to increase along on the y axis, then the violin shape is created by mirroring the density. The width of the violin will now be twice the length that would be have been measured vertically in a density plot. The lines overlaid in each plot represent the smoothed linear model of the amount of faces, it can be seen that all APIs take longer to complete detection of faces in an image when there are more faces.

As seen in the facets of Figure \ref{fig:timeFigure} times taken to search are varied between APIs, but Skybiometry consistently spent less time than other APIs. Microsoft and Google's times vary regardless of the number of faces found.
